Supplementary Information -- Morphological convergence as on-line lexical analogy

### 2020-04-24 supplementary_information/si.Rnw
na

# takes lmer fit, spits out coef table with ast
niceCoefTable = function(fit){
  my_table = fit %>% 
    tidy %>% 
    filter(
      group == 'fixed'
    ) %>% 
    mutate(
      sig = case_when(
        p.value >= 0.05 ~ 'n.s.',
        p.value < 0.05 & p.value >= 0.01 ~ '*',
        p.value < 0.01 & p.value >= 0.001 ~ '**',
        p.value < 0.001 ~ '***'
      )
    ) %>% 
    select(
      - p.value,
      - group
    )
return(my_table)  
}

@@

To calculate the similarity between two words, we first compute their dissimilarity. This is achieved using the string-edit (Levenshtein) distance, which is the smallest number of changes needed to transform one word into the other. Costs range from 0 (the corresponding segments are identical) to 1 (inserting or deleting an entire segment). Following \cite{albright2003rules} and \cite{dawdy2014learnability}, costs between 0 and 1 are assigned to corresponding segments that are not identical, based on how much the segments differ.

>>>>

# takes lmer fit, spits out coef table with ast
niceCoefTable = function(fit){
  my_table = fit %>% 
    tidy %>% 
    filter(
      group == 'fixed'
    ) %>% 
    mutate(
      sig = case_when(
        p.value >= 0.05 ~ 'n.s.',
        p.value < 0.05 & p.value >= 0.01 ~ '*',
        p.value < 0.01 & p.value >= 0.001 ~ '**',
        p.value < 0.001 ~ '***'
      )
    ) %>%
    rename(`Z score` = statistic) %>% 
    select(
      - p.value,
      - group
    )
return(my_table)  
}

@@

To calculate the similarity between two words, we first compute their dissimilarity. This is achieved using the string-edit (Levenshtein) distance, which is the smallest number of changes needed to transform one word into the other. For one unit of edit distance, these costs range from 0 (the corresponding segments are identical) to 1 (inserting or deleting an entire segment). Following \cite{albright2003rules} and \cite{dawdy2014learnability}, costs between 0 and 1 are assigned to corresponding segments that are not identical, based on how much the segments differ.
